---
title: "Search Analytics"
output: html_notebook
---

```{r packages}
library(ggplot2)
library(plyr)
```


```{r load data}
cjail = read.csv('../data/cash_bail_full.csv', stringsAsFactors=FALSE)
```

```{r preprocessing}
cjail$publish_date = mapply(as.Date, x=cjail$publish_date)
cjail$year = floor(cjail$publish_date / 365)
```


MediaCloud search focused on titles mentioning incarceration-related terms and covid-related terms: title:((coronavirus OR COVID\* OR SARS) AND (jail OR prison\* OR incarc\* OR detain\* OR offend\* OR inmate\* OR "correctional facility" OR "detention center") NOT Weinstein\* NOT Exotic\* NOT Tekashi\* NOT 6ix9ine\* NOT Tiger\* NOT Avenatti\* NOT "R. Kelly\*" NOT Melly\* NOT Shkreli\* NOT Manafort\* NOT "Bernie Madoff\*" NOT "Michael Cohen\*") AND tags_id_stories:8878461

```{r search}
# Search text
pattern = "death"
cjail$search_txt = mapply(grepl, pattern=pattern, x=cjail$new_text)
cjail$search_title = mapply(grepl, pattern=pattern, x=cjail$raw_title)

cjail$search = (cjail$search_txt | cjail$search_title)
print(sum(cjail$search) / nrow(cjail))
```


```{r}
# Order data
search_over_time = cjail[order(cjail$publish_date), c("publish_date", "search", "year")]

## Search numbers
# Count of search over time, reset each year
search_over_time_peryear = ddply(search_over_time, .(year), summarize, cumsum(search))
colnames(search_over_time_peryear) = c("year", "search_count")
search_over_time_peryear$day = search_over_time$publish_date %% 365
# Total search for each year
max_search_by_yr = ddply(search_over_time_peryear, .(year), summarize, max(search_count))
colnames(max_search_by_yr) = c("year", "annual_search_cnt")


## Count numbers
# Count over time, reset each year
search_over_time$counter = 1
counter_over_time_peryear = ddply(search_over_time, .(year), summarize, cumsum(counter))
colnames(counter_over_time_peryear) = c("year", "total_count")
cnt_by_yr = ddply(counter_over_time_peryear, .(year), summarize, max(total_count))
colnames(cnt_by_yr) = c("year", "annual_cnt")
search_over_time_peryear$counter = NULL


## Combine above data
search_over_time_peryear = merge(search_over_time_peryear, max_search_by_yr, all=TRUE)
search_over_time_peryear$total_count = counter_over_time_peryear$total_count
search_over_time_peryear = merge(search_over_time_peryear, cnt_by_yr, all=TRUE)

## Normalize
search_over_time_peryear$search_count_norm = search_over_time_peryear$search_count / search_over_time_peryear$annual_search_cnt

search_over_time_peryear$total_count_norm = search_over_time_peryear$total_count / search_over_time_peryear$annual_cnt
```


```{r}
ggplot() + 
  geom_line(data = search_over_time_peryear,
            aes(x = day, y = search_count_norm),
            color = "blue") + 
  geom_line(data = search_over_time_peryear,
            aes(x = day, y = total_count_norm), 
            color = "red") + 
  facet_grid(~search_over_time_peryear$year) + 
  ggtitle(pattern)

```

